### 2017-04-28 paper2.tex
Add files via upload

\chapter{A climatology of urban surface heat islands derived from hemispherical radiometric surface temperatures}

@@

The temperature of the surface is integral in understanding, predicting, and modeling boundary-layer air temperature patterns, surface energy balances, and, in urban areas, has important implications for human thermal comfort and building energy usage. Urban modification of surface geometry and thermal, radiative, moisture, and aerodynamic properties results in differential surface heating and cooling patterns and strong microscale spatiotemporal variations in urban surface temperature (T\textsubscript{surf}). Integrated up to larger scales, urban areas tend to store and generate more heat relative to non-built surroundings which manifests in elevated T\textsubscript{surf} and T\textsubscript{air} a phenomenon termed the urban heat island effect (UHI). To foster a more complete understanding of the effect of urban areas climates across scales, accurate, spatiotemporally continuous and geometrically representative characterization of T\textsubscript{surf} in cities has long been a goal in urban climatology. The proliferation of satellite and aerial thermal infrared (TIR) remote sensing has enabled spatially-extensive characterizations of surface climates at ever improving spatial and spectral resolutions. Such campaigns have elucidated urban T\textsubscript{surf} and surface urban heat island (sUHI) patterns globally at large spatial scales. However, technological improvements in TIR remote sensing have yet to address a three potential sources of error when applied in urban areas:

\begin{enumerate}
	\item Geometric undersampling of 3-dimensional terrain
	\item Temporal discontinuity in overpass cycles and sensor sampling regimes
	\item Clear-sky bias
\end{enumerate}

@@

Inter-site comparison is the crux of UHI analysis, thus it is imperative that urban T\textsubscript{surf} measurements are representative of coherent urban patches and free from confounding influences (i.e. atmospheric and emissivity effects). Meta-analysis of air temperature (T\textsubscript{air}) UHI literature shows that these goals are rarely satisfied \citep{Stewart2011}. Given the relative difficulty in retrieving accurate, representative urban T\textsubscript{surf}, similar conclusions are likely for sUHI analysis. In spite of this fact, and the short period over which large-scale, generalizable methods for measuring urban T\textsubscript{surf} have been available, study of sUHI via TIR remote sensing has expanded significantly in the last twenty years \citep{Peng2012,Voogt2003}. Using the method described in Chapter \ref{paper1} we derive an 8-month climatology of hemispherical radiometric urban T\textsubscript{surf} (T\textsubscript{hem, r}) from time continuous near-ground upwelling TIR as measured from an inverted pyrgeometer. The method was developed to address and overcome biases inherent in traditional methods for urban T\textsubscript{surf} retrieval by providing temporally continuous, geometrically representative\footnote{A hemispherical view is not perfectly geometrically representative of urban surface geometry. This is best illustrated by visualizing an urban area from the perspective of a downward facing ‘fish-eye’ camera. Geometric sampling biases are a result of lens distortions and the sensor cosine response. However, by sampling the surface 3-dimensionally, T\textsubscript{hem, r} is more representative of urban geometry than conventional 2-dimensional views of the surface. The geometric representivity of urban T\textsubscript{hem, r} is discussed in section \ref{Methodological limitations and considerations}.} urban T\textsubscript{surf} under all-sky conditions for sUHI analysis. These measurements are often made as a part of the net radiation determination for urban energy balance studies.

\subsection{Bias in thermal remote sensing}
Geometric biases in remote sensing of the urban surface are a result of its 3-dimensional, convoluted structure. Compared to flat terrain, complex urban surface geometry modifies receipt of incoming solar radiation and traps a portion of reflected solar and outgoing terrestrial radiation. The resulting microscale spatiotemporal contrasts in urban T\textsubscript{surf} create a directional dependence in observed urban T\textsubscript{surf} when measured from conventional narrow-field-of-view (FOV) TIR remote sensing platforms. Thus, remote sensed urban T\textsubscript{surf} varies based on sensor FOV, viewing angle and direction, and sun-surface geometry - this directional dependence of urban surface temperature is termed "effective thermal anisotropy" \citep{Voogt1998a}. Traditional satellite or airborne remote sensing platforms, by viewing the surface in the nadir, sample only a fraction of the complete urban surface and fail to capture this effect - leading to spatiotemporally variant directional biases of up to 10 \si{\kelvin} in observed urban T\textsubscript{surf} \citep{Voogt1995}. In general, geometric undersampling by a remote sensor in the nadir manifests as an overestimation of daytime T\textsubscript{surf} and an underestimation of nighttime T\textsubscript{surf} \citep{Adderley2015}. However, the magnitude and diurnal and seasonal behaviors of this bias are dependent on sensor viewing geometry and unique site characteristics (canyon height-to-width ratio, canyon orientation and materials, vegetation coverage, etc.). Thus, parameterization schemes to account for urban effective anisotropy are difficult to generalize across urban sites, sensor types, and sensor-surface geometries.

In addition to undersampling the urban surface, most thermal remote sensing platforms yield an instantaneous ‘snap-shot’ and cannot characterize time-continuous T\textsubscript{surf} patterns without sacrificing ground resolution. Temporal discontinuities in thermal remote sensing result in myriad of potential sources of bias over a wide range of time scales. Aerial and satellite thermal remote sensing require clear sky conditions (clouds are opaque with respect to thermal infrared radiation). Hence, long term satellite characterizations of sUHI are biased towards conditions that maximize urban-rural contrasts in T\textsubscript{surf}. This results in an overestimation of “all-sky” sUHI. At diurnal scales, satellite overpass cycles rarely coincide with sUHI maximums and are not standard across cities or platforms. Thus, analysis of sUHI patterns and magnitudes across cities and instrument platforms is difficult. At smaller time scales still, time-continuous analysis of urban T\textsubscript{surf} shows significant microscale (second to minute) fluctuations in temperature \citep{Christen2012}. Most thermal remote sensors provide instantaneous T\textsubscript{surf} (rather than temporally averaged) and are potentially contaminated by high-frequency microscale fluctuations in urban T\textsubscript{surf}. This is particularly salient in urban environments, where a large variety of fabric materials can produce significant directional contrasts in thermal admittance - and thus spatial variations in the magnitude of microscale fluctuations depending on the facet material types viewed by the sensor. The effect of this phenomenon on thermal remote sensing has not been extensively studied, however, the magnitude of microscale fluctuations in T\textsubscript{surf} is significant relative to a typical sUHI signal and thus constitutes a potentially large source of bias.

Both geometric and temporal shortcomings limit the representativity of traditional remote sensed evaluations of urban T\textsubscript{surf} and sUHI. The magnitude of these biases has not been extensively studied, particularly from a long term, climatological perspective. This study presents the first time-continuous, climatological analysis of sUHI retrieved from radiometric hemispherical urban T\textsubscript{surf} retrieved via the correction method described in Chapter \ref{paper1}. These measures are used to assess the magnitude of and overcome geometric and temporal biases inherent in urban TIR remote sensing.

@@

This section describes the study area and provides a brief overview of the multiple line-of-sight atmospheric correction method used to derive a time-continuous eight month climatology urban T\textsubscript{hem, r} for sUHI analysis. A thorough discussion of the method is included in Chapter \ref{paper1}.

@@

First, surface-to-sensor path length and view factor geometries are calculated with the surface-sensor-sun urban model (SUM) \citep{Soux2004}. Using a digital building model, SUM calculates path lengths from the surface to the sensor and angular view factors by projecting the pyrgeometer FOV onto a simplified (orthogonal) representation of the surface, determining which points in the DBM are 'seen' by the sensor, and calculating the distance from each 'seen' point to the sensor. Path lengths are binned at 5\si{\degree} intervals and averaged over the azimuth angle. Finally, view factors are calculated for each 5\si{\degree} angular as each bin's proportion of the total view factor and normalized to unity.

Second, version 4.1 of the MODTRAN radiative transfer code \citep{Berk1987} is used to model spectral at-sensor radiances for each angular path length. Runs are initialized using profiles of T\textsubscript{air} and water vapor content collected concurrently at each time step. Spectral radiances are modeled over a bandpass of 1 to 2500 \si{cm^{-1}} at an emissivity of 0.95 and convolved by an extended dome transmittance function to ensure that modeled radiances replicate the actual remote sensed signal. Consultation with radiometer manufacturers made clear the need to extend the modeled bandpass beyond a typical longwave bandpass (approximately 250 - 2500 \si{cm^{-1}}), as silicone domed pyrgeometers are transmissive of radiation in much shorter wavenumber (longer wavelengths) than 250 \si{cm^{-1}} (40 \si{\micro\meter}).

Third, radiances for each angular path length are integrated over the waveband and multiplied their respective normalized view factors. Weighted and corrected angular radiances are integrated over the hemisphere to yield a modeled at-sensor irradiance as ‘seen’ by the pyrgeometer for the target T\textsubscript{hem, r}.

For each time step, the above steps are repeated at an interval of 0.5 \si{\kelvin} for a predefined range of potential T\textsubscript{hem, r}, with results aggregated into a lookup table relating modeled irradiances to corrected T\textsubscript{hem, r} for the observed ambient T\textsubscript{air} and humidities. The measured irradiance is then matched with the closest modeled irradiance to return the associated corrected T\textsubscript{hem, r} for the target time step. sUHI magnitudes for the study area are calculated as the difference between urban T\textsubscript{hem, r} and rural T\textsubscript{hem, b} with rural T\textsubscript{hem, b} calculated via

@@

\noindent where $L_z^\uparrow$ is at-sensor upwelling longwave radiation, $L_{sky}^\downarrow$ is at-sensor reflected downwelling longwave radiation, and emissivity ($\epsilon$) = 0.98.

@@

@@

During an intensive observation period (IOP) in late June/early July 2002, the Sperrstrasse canyon was instrumented with an array of infrared thermometers (IRT) to view individual canyon facet T\textsubscript{surf} to sample representative road, roof, and wall surface temperatures (T\textsubscript{road}, T\textsubscript{roof}, and T\textsubscript{wall} respectively). Plan and complete aspect ratios for the Sperrstrasse canyon are used to compute weighting schemes to retrieve complete and plan surface temperatures (T\textsubscript{comp} and T\textsubscript{plan} respectively) at 30 minute intervals over the IOP. T\textsubscript{comp} represents an area weighted average complete urban T\textsubscript{surf}, while T\textsubscript{plan} represents the Sperrstrasse site as viewed by a satellite or aerial remote sensor in the nadir. Weighting schemes for T\textsubscript{plan} and T\textsubscript{comp} are included in Table \ref{weightings}. Urban T\textsubscript{surf} derived from complete, plan, and hemispherical representations of the Sperrstrasse site are used to investigate the effect of sensor-surface geometry on remote sensed T\textsubscript{surf} and sUHI, and to quantify the magnitude of geometric biases time-continuously over a range of synoptic conditions. For comparison of sUHI to air temperature UHI, canopy layer air temperature UHI (clUHI) magnitudes are calculated as the difference between urban and rural T\textsubscript{air} measured from 2 \si{\meter} above ground level.

@@

Figure \ref{heatsuhi} shows seasonal variations in diurnal patterns of mean monthly hemispherical sUHI magnitudes at 30 minute intervals for the eight month study period. sUHI displays significant seasonal variation, particularly by day, and is strongly controlled by day length and solar angle. Nighttime sUHI does not vary significantly across seasons.

Figure \ref{heatcluhi} shows seasonal variations in diurnal patterns of mean monthly clUHI calculated at 30 minute intervals for the eight month study period. clUHI development is strongly controlled by the timing of sunset/sunrise cycles and displays the largest seasonal variance in the hours immediately after sunset. Daytime clUHI does not vary significantly across seasons. 
\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,height=7in,keepaspectratio]{heatsuhi}
	\caption{A heatmap of mean half hourly hemispherical sUHI for each month calculated at 30-minute intervals over the eight month study period.}
	\label{heatsuhi}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,height=7in,keepaspectratio]{heatatuhi}
	\caption{A heatmap of mean half hourly canopy layer UHI for each month calculated at 30-minute intervals from T\textsubscript{air} measured at approximately 2 \si{\meter} above ground level over the eight month study period.}
	\label{heatcluhi}
\end{figure}

>>>>

\begin{bibunit}

\rhead{\thepage}

\chapter{A climatology of urban surface heat islands derived from hemispherical radiometric surface temperatures}
\label{paper2}

@@

The temperature of the surface is integral in understanding, predicting, and modeling boundary-layer air temperature patterns, surface energy balances, and, in urban areas, has important implications for human thermal comfort and building energy usage. Urban modification of surface geometry and thermal, radiative, moisture, and aerodynamic properties results in differential surface heating and cooling patterns and strong microscale spatiotemporal variations in urban surface temperature (T\textsubscript{surf}). Integrated up to larger scales, urban areas tend to store more heat relative to non-built surroundings; traffic, HVAC systems, and industrial processes contribute to an additional anthropogenic heat input. These manifest in elevated T\textsubscript{surf} and T\textsubscript{air} in cities, a phenomenon termed the urban heat island effect (UHI). To foster a more complete understanding of the effect of urban areas on climates across a range of scales, accurate, spatiotemporally continuous and geometrically representative characterization of T\textsubscript{surf} in cities has long been a goal in urban climatology. The proliferation of satellite and aerial thermal infrared (TIR) remote sensing has enabled spatially-extensive characterizations of surface climates at ever improving spatial and spectral resolutions. Such campaigns have elucidated urban T\textsubscript{surf} and surface urban heat island (sUHI) patterns globally at large spatial scales \cite{Peng2012,Zhao2014}. However, technological improvements in TIR remote sensing have yet to address three potential sources of error that arise when applied in urban areas:

\begin{enumerate}
	\item Geometric undersampling of 3-dimensional surface structure
	\item Satellite overpass cycles and sensor sampling regimes that result in temporal discontinuity of the surface temperature time series
	\item Clear-sky bias that contribute to an overestimation of "all-sky" surface temperatures
\end{enumerate}

@@

Inter-site comparison is the crux of UHI analysis, thus it is imperative that urban T\textsubscript{surf} measurements are representative of coherent urban patches and free from confounding influences (i.e. atmospheric and emissivity effects). Meta-analysis of the air temperature (T\textsubscript{air}) UHI literature shows that these goals are rarely satisfied \citep{Stewart2011}. Given the relative difficulty in retrieving accurate, representative urban T\textsubscript{surf}, similar conclusions are likely for sUHI analysis. In spite of this fact, and the short period over which large-scale, generalizable methods for measuring urban T\textsubscript{surf} have been available, study of sUHI via TIR remote sensing has expanded significantly in the last twenty years \citep{Peng2012,Voogt2003}. Using the method described in Chapter \ref{paper1} an 8-month climatology of hemispherical radiometric urban T\textsubscript{surf} (T\textsubscript{hem, r}) was derived from time continuous near-ground upwelling TIR as measured from an inverted pyrgeometer. The method was developed to address and overcome biases inherent in traditional methods for urban T\textsubscript{surf} retrieval by providing temporally continuous, geometrically representative\footnote{A hemispherical view is not perfectly geometrically representative of urban surface geometry. This is best illustrated by visualizing an urban area from the perspective of a downward facing ‘fish-eye’ camera. Geometric sampling biases are a result of lens distortions and the sensor cosine response. However, by sampling the surface 3-dimensionally, T\textsubscript{hem, r} is more representative of urban geometry than conventional 2-dimensional views of the surface. The geometric representivity of urban T\textsubscript{hem, r} is discussed in section \ref{Methodological limitations and considerations}.} urban T\textsubscript{surf} under all-sky conditions for sUHI analysis. These measurements are often made as a part of the net radiation determination for urban energy balance studies.

\subsection{Bias in thermal remote sensing}
Geometric biases in remote sensing of the urban surface are a result of its 3-dimensional, convoluted structure. Compared to flat terrain, complex urban surface geometry modifies receipt of incoming solar radiation and traps a portion of reflected solar and outgoing terrestrial radiation. The resulting microscale spatiotemporal contrasts in urban T\textsubscript{surf} create a directional dependence in observed urban T\textsubscript{surf} when measured from conventional narrow-field-of-view (FOV) TIR remote sensing platforms. Thus, remote sensed urban T\textsubscript{surf} varies based on sensor FOV, viewing angle and direction, and sun-surface geometry. This directional dependence of urban surface temperature is termed "effective thermal anisotropy" \citep{Voogt1998a}. Traditional satellite or airborne remote sensing platforms, by viewing the surface in the nadir, sample only a fraction of the complete urban surface, leading to spatiotemporally variant directional biases in remote sensed urban T\textsubscript{surf} of up to 10 \si{\kelvin} \citep{Voogt1995}. In general, geometric undersampling by a remote sensor in the nadir manifests as an overestimation of daytime T\textsubscript{surf} and an underestimation of nighttime T\textsubscript{surf} \citep{Adderley2015}. However, the magnitude and diurnal and seasonal behaviors of this bias are dependent on sensor viewing geometry and unique site characteristics (canyon height-to-width ratio, canyon orientation and materials, vegetation coverage, etc.). Thus, parameterization schemes to account for urban effective anisotropy are difficult to generalize across urban sites, sensor types, and sensor-surface geometries.

In addition to undersampling the urban surface, most thermal remote sensing platforms yield an instantaneous ‘snap-shot’ and cannot characterize time-continuous T\textsubscript{surf} patterns without sacrificing ground resolution. Temporal discontinuities in thermal remote sensing result in myriad potential sources of bias over a wide range of time scales. Aerial and satellite thermal remote sensing require clear sky conditions (clouds are opaque with respect to thermal infrared radiation). Hence, long term satellite characterizations of sUHI are biased towards conditions that maximize urban-rural contrasts in T\textsubscript{surf}. This results in an overestimation of “all-sky” sUHI. At diurnal scales, satellite overpass cycles rarely coincide with sUHI maximums and are not standard across cities or platforms. Thus, analysis of sUHI patterns and magnitudes across cities and instrument platforms is difficult. At shorter time scales still, time-continuous analysis of urban T\textsubscript{surf} shows significant microscale (second to minute) fluctuations in temperature \citep{Christen2012}. Most thermal remote sensors provide instantaneous T\textsubscript{surf} (rather than temporally averaged) and are potentially contaminated by high-frequency microscale fluctuations in urban T\textsubscript{surf}. This is particularly salient in urban environments, where a large variety of fabric materials can produce significant spatial contrasts in thermal admittance (for instance, roof materials tend to have much lower thermal admittances than wall or road materials. Such large spatial contrasts in thermal admittance are generally not present in non-urban or rural environments). As a result, the magnitude of potential biases in remote sensed urban T\textsubscript{surf} from microscale fluctuations depends on the facet material types viewed by the sensor and can change with viewing direction and sensor FOV. The effect of this phenomenon on thermal remote sensing has not been extensively studied, however, the magnitude of microscale fluctuations in T\textsubscript{surf} is significant relative to a typical sUHI signal and thus constitutes a potentially large source of bias.

Both geometric and temporal shortcomings limit the representativity of traditional remote sensed evaluations of urban T\textsubscript{surf} and sUHI. The magnitude of these biases has not been extensively studied, particularly from a long term, climatological perspective. These biases lead us to ask: What is the nature of the true sUHI? How does it vary temporally and over a full range of weather conditions? To address these questions, this study presents the first time-continuous, climatological analysis of sUHI retrieved from radiometric hemispherical urban T\textsubscript{surf} retrieved via the correction method described in Chapter \ref{paper1}. These measures are used to assess the magnitude of and overcome geometric and temporal biases inherent in urban TIR remote sensing.

@@

This section describes the study area and provides a brief overview of the multiple line-of-sight atmospheric correction method used to derive a time-continuous eight month climatology of urban T\textsubscript{hem, r} for sUHI analysis. A thorough discussion of the method is included in Chapter \ref{paper1}.

@@

First, surface-to-sensor path length and view factor geometries are calculated with the surface-sensor-sun urban model (SUM) \citep{Soux2004}. Using a digital building model, SUM calculates path lengths from the surface to the sensor and angular view factors by projecting the pyrgeometer FOV onto a simplified representation of the surface, determining which points in the DBM are 'seen' by the sensor, and calculating the distance from each 'seen' point to the sensor. Path lengths are binned at 5\si{\degree} intervals and averaged over the azimuth angle. Finally, view factors are calculated for each 5\si{\degree} angular as each bin's proportion of the total view factor and normalized to unity.

Second, version 4.1 of the MODTRAN radiative transfer code \citep{Berk1987} is used to model spectral at-sensor radiances for each angular path length. Runs are initialized using profiles of T\textsubscript{air} and water vapor content collected concurrently at each time step. Spectral radiances are modeled over a bandpass of 1 to 2500 \si{cm^{-1}} at an emissivity of 0.95 and convolved by an extended dome transmittance function to ensure that modeled radiances replicate the actual remote sensed signal. Consultation with radiometer manufacturers made clear the need to extend the modeled bandpass beyond a typical longwave bandpass (approximately 250 - 2500 \si{cm^{-1}}), as silicone domed pyrgeometers transmit radiation at much smaller wavenumbers (longer wavelengths) than 250 \si{cm^{-1}} (40 \si{\micro\meter}).

Third, radiances for each angular path length are integrated over the waveband and multiplied by their respective normalized view factors. Weighted and corrected angular radiances are integrated over the hemisphere to yield a modeled at-sensor irradiance as ‘seen’ by the pyrgeometer for the target T\textsubscript{hem, r}.

For each time step, these steps are repeated at an interval of 0.5 \si{\kelvin} for a predefined range of potential T\textsubscript{hem, r}, with results aggregated into a lookup table relating modeled irradiances to corrected T\textsubscript{hem, r} for the observed ambient T\textsubscript{air} and humidities. The measured irradiance is then matched with the closest modeled irradiance to return the associated corrected T\textsubscript{hem, r} for the target time step. sUHI magnitudes for the study area are calculated as the difference between urban T\textsubscript{hem, r} and rural T\textsubscript{hem, b} with rural T\textsubscript{hem, b} calculated via

@@

\noindent where $L_z^\uparrow$ is at-sensor upwelling longwave radiation, $L_{sky}^\downarrow$ is at-sensor reflected downwelling longwave radiation, and emissivity ($\epsilon$) = 0.94.

@@

\subsection{Evaluation and parameterization}

To evaluate the method

@@

During an intensive observation period (IOP) in late June/early July 2002, the Sperrstrasse canyon was instrumented with an array of infrared thermometers (IRT) to view individual canyon facet T\textsubscript{surf} to sample representative road, roof, and wall surface temperatures (T\textsubscript{road}, T\textsubscript{roof}, and T\textsubscript{wall} respectively). Plan and complete aspect ratios for the Sperrstrasse canyon are used to compute weighting schemes to retrieve complete and plan surface temperatures (T\textsubscript{comp} and T\textsubscript{plan} respectively) at 30 minute intervals over the IOP. T\textsubscript{comp} represents a complete urban T\textsubscript{surf}, where facet temperatures are weighted and averaged based on their areal proportion of the complete urban surface area. T\textsubscript{plan} represents the Sperrstrasse site as viewed by a satellite or aerial remote sensor in the nadir. Weighting schemes for T\textsubscript{plan} and T\textsubscript{comp} are included in Table \ref{weightings}. Urban T\textsubscript{surf} derived from complete, plan, and hemispherical representations of the Sperrstrasse site are used to investigate the effect of sensor-surface geometry on remote sensed T\textsubscript{surf} and sUHI, and to quantify the magnitude of geometric biases over a range of time scales and synoptic conditions. For comparison of sUHI to air temperature UHI, canopy layer air temperature UHI (clUHI) magnitudes are calculated as the difference between urban and rural T\textsubscript{air} measured from 2 \si{\meter} above ground level.

@@

Figure \ref{heatsuhi} shows seasonal variations in diurnal patterns of mean monthly hemispherical sUHI magnitudes at 30 minute intervals for the eight month study period. The sUHI displays significant seasonal variation, largest in the daytime hours, and is strongly controlled by day length and solar angle. Nighttime sUHI does not vary significantly across seasons.

Figure \ref{heatcluhi} shows seasonal variations in diurnal patterns of mean monthly clUHI calculated at 30 minute intervals for the eight month study period. clUHI development is strongly controlled by the timing of sunset/sunrise cycles and displays the largest seasonal variance in the hours immediately after sunset. Daytime clUHI does not vary significantly across seasons. 
\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,height=7in,keepaspectratio]{heatsuhi}
	\caption{A heatmap of mean half hourly hemispherical sUHI for each month calculated at 30 \si{\min} intervals over the eight month study period. Results are interpolated between months.}
	\label{heatsuhi}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,height=7in,keepaspectratio]{heatatuhi}
	\caption{A heatmap of mean half hourly canopy layer UHI for each month calculated at 30 \si{\min} intervals from T\textsubscript{air} measured at approximately 2 \si{\meter} above ground level over the eight month study period. Results are interpolated between months.}
	\label{heatcluhi}
\end{figure}

### 2017-04-28 uw-ethesis-frontpgs.tex
Add files via upload

% The rest of the front pages should contain no headers and be numbered using Roman numerals starting with `ii'
\pagestyle{plain}
\setcounter{page}{2}

@@

% D E C L A R A T I O N   P A G E
% -------------------------------
  % The following is a sample Delaration Page as provided by the GSO
  % December 13th, 2006.  It is designed for an electronic thesis.
  \noindent
I hereby declare that I am the sole author of this thesis. This is a true copy of the thesis, including any required final revisions, as accepted by my examiners.

  \bigskip

  \noindent
I understand that my thesis may be made electronically available to the public.

@@

\begin{center}\textbf{Acknowledgements}\end{center}

@@

% Change page numbering back to Arabic numerals
\pagenumbering{arabic}

>>>>

% The rest of the front pages should contain no headers and be numbered using Roman numerals starting with `ii'
\pagestyle{plain}
\setcounter{page}{3}

@@

@@

\begin{center}\textbf{Acknowledgments}\end{center}

@@

% Change page numbering back to Arabic numerals and have it in the upper right corner
\pagenumbering{arabic}
\renewcommand{\headrulewidth}{0pt}
\pagestyle{fancy}
\fancyhf{}
\rhead{\thepage}
\makeatletter
\let\ps@plain\ps@fancy % plain style = fancy style
\makeatother
